---
title: "A3"
author: "Xinrui Wang 1004741078"
date: "2021/7/22"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1
1. Y Poisson distribution
a) P (Y = 0) = 0.5 -> e^(-lambda)=0.5 --> lambda=-log(0.5)
in poisson distribution, mean = variance = lambda =
```{r}
-log(0.5)
```
b)P(X=3)=
```{r}
dpois(3,-log(0.5))
```
2. est P(H) = pi, x=9,n=15,x/n=0.6
a) Bin(n=15,theta=0.5) 
pdf:f(x|theta)=theta^x*(1-theta)^x
L(theta|x=9)=theta^9*(1-theta)^6

b)
```{r}
likelihood=function(n,y,theta){return(theta^y*(1-theta)^(n-y))}
theta=seq(0.01,1,0.01)
plot(theta,likelihood(15,9,theta),type = "l",ylab="Likelihood")

loglike=function(n,y,theta){return(y*log(theta)+(n-y)*log(1-theta))}
plot(loglike(15,9,theta)~theta,type="l", ylab="Log Likelihood")
abline(v=0.6)
```
MLE pi=
```{r}
which.max(loglike(15,9,theta))*0.01
```


## Q2
a)
```{r}
x<-seq(3,12,1)
pi<-c(0.03,0.06,0.12,0.23,0.4,0.6,0.77,0.88,0.94,0.97)
plot(pi~x)
```
not linear

b)
```{r}
plot(log(pi)~x)
```
not linear

c)
```{r}
logitpi<-pi/(1-pi)
plot(logitpi~x)
cor(x,logitpi)
```
not linear
d) none of the models above is linear though,   a) looks best fit the data 
```{r}
plot(glm(logitpi~x))
```

## Q3
```{r}
d=c(45,15,40,83,90,25,35,65,95,35,75,45,50,75,30,25,20,60,70,30,60,61,65,15,20,45,15,25, 15,30,40,15,135,20,40)
y=c(0,0,1,1,1,1,1,1,1,1,1,1,0,1,0,1,0,1,1,1,1,0,1,0,0,1,0,1,0,1,1,0,1,0,0)
```
a)
```{r}
model<-glm(y~d,family=binomial)
summary(model)
```
logit=-2.21+0.07*d
It means the sore threat on walking will increase by 0.0703 as the minute increase by 1.

b)
```{r}
exp(-2.21358+0.07038*1)/(1+exp(-2.21356+0.07038*1))
```
c)
```{r}
library(lmtest)
lrtest(model)
```
the possibility (p-value) is 0.0004 smaller than 0.05, we will reject null hypothesis:restricted model is good.
so unrestricted model is good.
